Fig4

### 2020-04-26 analysis/figure-4.Rmd
now with WGCNA results incorporated into fig 4

```{r setup}
library(tidyverse)
library(cowplot)
library(ggimage)
library(apaTables)
library(factoextra)

@@

## PRL hormone

```{r hormones}

# hormones
prolactin <- read_csv("../results/07_hormones.csv") %>%
    filter(study == "characterization", hormone %in% c("prolactin"))  %>% 
    droplevels() 
prolactin$treatment <- factor(prolactin$treatment, levels = alllevels)
```

@@

PRLpit <- candidatevsd %>% filter(tissue == "pituitary", gene == "PRL")
PRLpitF <- candidatevsd %>% filter(tissue == "pituitary", gene == "PRL", 
                                   sex == "female" , treatment != "control")
PRLpitM <- candidatevsd %>% filter(tissue == "pituitary", gene == "PRL", 
                                   sex == "male", treatment != "control")
```

@@

PRLvsd3 %>%
  group_by(sex, tissue, hiloPRL) %>%
  summarize(n = n())

@@

fig4 <- plot_grid(expdesign,d2m, ncol = 1, rel_heights = c(0.25,1))
fig4
```

>>>>

```{r setup}
library(tidyverse)
library(cowplot)
library(ggimage)
library(apaTables)
library(factoextra)
library(corrr)
library(ggpubr)

@@

@@

PRLpit <- candidatevsd %>% filter(tissue == "pituitary", gene == "PRL")
PRLpitF <- candidatevsd %>% filter(tissue == "pituitary", gene == "PRL", 
                                   sex == "female" , treatment != "control")
PRLpitM <- candidatevsd %>% filter(tissue == "pituitary", gene == "PRL", 
                                   sex == "male", treatment != "control")

PRLvsd3 %>%
  group_by(sex, tissue, hiloPRL) %>%
  summarize(n = n())
```

@@

@@

## resutls from WGCNA prl module

PRLgenes <- read_csv("../results/PRLmodule.csv") %>% pull(x)

candidatevsd <- getcandidatevsd(PRLgenes, "pituitary", sexlevels)

df <- candidatevsd %>%
    pivot_wider(names_from = gene, values_from = counts) %>%
    select(-sex,-tissue, -treatment, -samples) %>%
    correlate() %>%
  focus(PRL)  %>%
  arrange(rowname)
df

k <- df %>%
  filter(PRL > 0.65) %>% 
  mutate(PRLrounded = round(PRL, 2))%>% 
  ggplot(aes(x = reorder(rowname, PRL), y = PRL)) +
  geom_bar(stat = "identity") +
  theme_B3() +
  theme(axis.text.y = element_text(face = "italic")) +
  labs(x = " ", y = "Correlation with PRL", subtitle = "Female and male pituitary") +

  coord_flip() +
  scale_y_continuous(expand = c(0, 0))

l <- candidatevsd %>%
  filter(gene == "LAPTM4B", treatment != "control") %>%
  ggplot(aes(x = treatment, y = counts, fill = treatment, color = sex)) +
  geom_boxplot() +
  scale_fill_manual(values = allcolors) +
  scale_color_manual(values = allcolors)  +
  theme_B3()  +
  theme(legend.position = "none", axis.title.y = element_text(face = "italic")) +
  labs(x = "Parental stage", y = "LAPTM4B", subtitle = " " )

m <- candidatevsd %>%
  filter(gene %in% c("LAPTM4B", "PRL"),  treatment != "control") %>%
  pivot_wider(names_from = gene, values_from = counts) %>%
  ggplot(aes(x = PRL, y = LAPTM4B)) +
  geom_point(aes(color = treatment)) +
  geom_smooth(aes(color = sex), method = "lm") +
  scale_fill_manual(values = allcolors) +
  scale_color_manual(values = allcolors)  +
  theme_B3() +
  theme(axis.title = element_text(face = "italic"),
        legend.position = "none") +
  stat_cor( size = 2) + labs(subtitle = " ")

klm <- plot_grid(k,l,m, rel_widths = c(1,1,0.75), nrow = 1, 
                 labels = c("N", "O", "P"), label_size = 8)

fig4 <- plot_grid(expdesign,d2m, klm, ncol = 1, rel_heights = c(0.25, 0.75, 0.4))
fig4
```
